Equivalence Hypergraphs:\\ Semantics of E-Graphs and their Generalization to Monoidal Theories

### 2023-10-01 main.tex
test
some clean-up

\documentclass
  [ acmsmall
  , pdftex
  , dvipsnames
  , review
  , nonacm
  , screen
  , authordraft
  ]{acmart}

@@

% quiver is for quiver figures
\usepackage{quiver}
\usepackage{tikz}
\usepackage{tikz-network}
\usepackage{amsthm}
\usepackage{xspace}
\usepackage{xargs}
\usepackage[
  colorinlistoftodos,
  prependcaption,
  % disable,
]{todonotes}
\usepackage{fontenc}

@@

\usepackage{mathtools,mathrsfs}
\usepackage{tikz-cd}
\usepackage{tikzit}

@@

\title{Equivalence Hypergraphs: Semantics of E-Graphs and their Generalization to Monoidal Theories}
\author{Chris Barrett, Dan Ghica, Aleksei Tiurin}

@@

% some sections might be commented out as overleaf compilation times out.

% \input{sections/introduction}
\input{sections/categorical_semantics}
\input{sections/combinatorial_semantics}

\input{sections/soundness_and_completeness}

\input{sections/e-graph-translation}
\input{sections/conclusion}

>>>>

\documentclass
  [ acmsmall
  , pdftex
  , dvipsnames
  , review
  , nonacm
  , screen
  % , authordraft
  ]{acmart}

@@

% quiver is for quiver figures
% \usepackage{quiver}
\usepackage{tikz}
\usepackage{tikz-network}
\usepackage{xspace}
\usepackage{xargs}
\usepackage[
  colorinlistoftodos,
  prependcaption,
  % disable,
]{todonotes}
\usepackage{fontenc}

@@

% \usepackage{mathtools,mathrsfs}
\usepackage{tikz-cd}
\usepackage{tikzit}

@@

\title{Equivalence Hypergraphs:\\ Semantics of E-Graphs and their Generalization to 
Monoidal Theories}
\author{Chris Barrett, Dan Ghica, Aleksei Tiurin}

@@

\input{sections/introduction}
\input{sections/categorical_semantics}
\input{sections/combinatorial_semantics}
\input{sections/soundness_and_completeness}
\input{sections/e-graph-translation}
\input{sections/conclusion}
